### 2016-06-04 w-wires/paper_gerasimovda.tex
fixed proof for 0 < y < Z

@@

@@

\[
\ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R - C + y}} \frac{1}{\sqrt{R + C - y}}
\]

Replace:
\begin{itemize}
\item $R^2 - C^2 + 2 (C + 1) y + 1$ with its minimum value $R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1$
\item $R - C + y$ with its minimum value $R - C + \frac{V}{4}$
\item $R + C - y$ with its minimum value $R + C - Z$
\end{itemize}

Function $\ln^2(x)$ is integrable in the neighbourhood of $0$ and it is well known \todo{reference?} that

@@

In our case, $x_0 = \frac{V}{4}$, $b = Z$, therefore the integral is bounded by constant independent of $R$ and $C$. Therefore, the behaviour of the function is defined by the behaviour of its multiplier before the integral:

@@

As $r \to \infty$, clearly $R \to \infty$, $C \to \infty$, $R - C \to 0$ and one can easily see that the expression above is $\mcO(\frac{1}{\sqrt{R + C}})$, therefore, zero in the limit.

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
 % \todo{proof? just take a look at second derivative?}
Since $s_1$ is concave, strictly increasing and for fixed $r$, our domain of interest is only $\Im k \le C + R$, we estimate the function from below by a linear function $s_4$:

@@

\todo{Ask Popov? Add to slides?? Unit cicle in Cayley space maps to $R$, and $\ln\abs{\det S}$ on $R$ is zero everywhere}

@@

To estimate, we will split the integration in three parts:

>>>>

\todo{Ask Popov? Add to slides?? Unit cicle in Cayley space maps to $R$, and $\ln\abs{\det S}$ on $R$ is zero everywhere}
\todo{Prove about zeroes separate by finite intervals?}
\todo{Prove about arbitrary linear function?}

@@

First we will compute an upper bound for the integrand. Notice that for $0 \le y \le \frac{V}{4}$:

\todo{???}
\begin{align*}
    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} \\
\le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\end{align*}

@@

First we will compute an upper bound for the integrand. Notice that for $\frac{V}{4} \le y < Z$:

\begin{align*}
    & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + y}} 
\\ \le & \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
\\ \le & \ln^2 \left( \frac{1}{2 V}(V^2 - 1) (y - Z) \right) \frac{R}{R^2 - C^2 + 2 (C + 1) \frac{V}{4} + 1} \frac{1}{\sqrt{R + C - Z}} \frac{1}{\sqrt{R - C + \frac{V}{4}}}
\end{align*}

Function $\ln^2(x)$ is integrable in the neighbourhood of $x = 0$ and it is well known \todo{reference?} that

@@

In our case, $x_0 = \frac{V}{4}$, $b = Z$, therefore $x_0 - b \ne 0$ and the integral is bounded by a constant independent of $R$ and $C$. Therefore, the behaviour of the function is defined by the behaviour of its constant multiplier:

@@

As $r \to \infty$, clearly $R \to \infty$, $C \to \infty$, $R - C \to 0$ and one can easily see that the expression above is $\mcO(\frac{1}{\sqrt{R + C}})$, therefore, zero in the limit. \todo{dependency on $r$ everywhere???}

@@

% TODO
% https://proofwiki.org/wiki/Inverse_of_Strictly_Increasing_Strictly_Concave_Real_Function_is_Strictly_Convex
 % \todo{proof? just take a look at second derivative?}
Since $s_1$ is concave, strictly increasing and for fixed $r$, our domain of interest is only $\Im k \le C + R$, we estimate the function from below by a linear function $s_4$: \todo{plot?}

@@

@@

To estimate, we will split the inegral in three parts:
